PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-06 paper/sec-results.tex
Move low-statistics plot into an appendix

The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
$\mu_\mathrm{F}$, are chosen, for each process, as follows. In the case of Drell--Yan
lepton pair production, we use the fixed scale $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
the mass of the Z boson, for the ATLAS measurement, and the scale
$\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
invariant mass bin, for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_\mathrm{R}=\mu_\mathrm{F}=H_\mathrm{T}/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_\mathrm{T}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}+\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^{\bar{\mathrm{t}}})}$, with $m_\mathrm{t}$,
$p_\mathrm{T}^\mathrm{t}$ and $p_\mathrm{T}^{\bar{\mathrm{t}}}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of Z-boson production with non-zero transverse momentum, we use
$\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted in the Monte Carlo generation upon scale
variations. To this purpose, we use the default \textsc{MG5\_aMC}
implementation, whereby the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
from the nine-point scale variations is constructed. However, we note that
\textsc{PineAPPL} allows the user to determine the envelope with any point
prescription, see appendix~\ref{app:pineappl-demo} for an example.

@@

%-------------------------------------------------------------------------------
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB_lowstat}\\
    \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
      high-mass Drell--Yan lepton pair measurement in the high-mass region at
      a centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The first panel
      displays the relative difference (in per mille) between the {\sc PineAPPL}
      and the MC results for the central, upper and lower scale choices,
      for theories accurate to both NLO QCD and NLO QCD+EW. The second, third
      and fourth panels present the theoretical predictions, accurate to either
      NLO QCD or NLO QCD+EW, always normalised to the former; on top of the
      theoretical predictions, the PDF uncertainty, the scale uncertainty and
      the Monte Carlo uncertainty are displayed in turn. The relative
      uncertainty of the experimental data is also shown for comparison.}
    \label{fig:atlaszhighmass49fb}
\end{figure}
%-------------------------------------------------------------------------------

>>>>

The central values of the renormalisation and factorisation scales, $\mu_\mathrm{R}$ and
$\mu_\mathrm{F}$, are chosen, for each process, as follows. In the case of Drell--Yan
lepton pair production, we use the fixed scale $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where $M_\mathrm{Z}$ is
the mass of the Z boson, for the ATLAS measurement, and the scale
$\mu_\mathrm{R}=\mu_\mathrm{F}=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
invariant mass bin, for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_\mathrm{R}=\mu_\mathrm{F}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_\mathrm{R}=\mu_\mathrm{F}=H_\mathrm{T}/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_\mathrm{T}=\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^\mathrm{t})^2}+\sqrt{m_\mathrm{t}^2+(p_\mathrm{T}^{\bar{\mathrm{t}}})}$, with $m_\mathrm{t}$,
$p_\mathrm{T}^\mathrm{t}$ and $p_\mathrm{T}^{\bar{\mathrm{t}}}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of Z-boson production with non-zero transverse momentum, we use
$\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted on-the-fly in the Monte Carlo generation upon scale
variations, with the technique presented in Ref.~\cite{Frederix:2011ss}. To this purpose, we use the default \textsc{MG5\_aMC}
implementation, whereby the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$, and the envelope
from the nine-point scale variations is constructed. However, we note that
\textsc{PineAPPL} allows the user to determine the envelope with any point
prescription, see appendix~\ref{app:pineappl-demo} for an example.

@@

%-------------------------------------------------------------------------------
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLASZHIGHMASS49FB}\\
    \caption{Validation and test of the \textsc{PineAPPL} grid for the ATLAS
      high-mass Drell--Yan lepton pair measurement in the high-mass region at
      a centre-of-mass energy of \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The first panel
      displays the relative difference (in per mille) between the {\sc PineAPPL}
      and the MC results for the central, upper and lower scale choices,
      for theories accurate to both NLO QCD and NLO QCD+EW. The second, third
      and fourth panels present the theoretical predictions, accurate to either
      NLO QCD or NLO QCD+EW, always normalised to the former; on top of the
      theoretical predictions, the PDF uncertainty, the scale uncertainty and
      the Monte Carlo uncertainty are displayed in turn. The relative
      uncertainty of the experimental data is also shown for comparison.}
    \label{fig:atlaszhighmass49fb}
\end{figure}
%-------------------------------------------------------------------------------
